---
title: "HF Statistics 5"
output: html_notebook
---


##이산확률분포 사용하기

```{r}
pic = c("dollar", "cherry", "lemon", "ETC")
per = c(0.1, 0.2, 0.2, 0.5)

d1 <- data.frame(pic, per)
d1
```



```{r}
combi = c("3dollars", "2dollars&1cherry","3cherrys", "3lemons", "NONE")
prize = c(20, 15, 10, 5, 0)
prob = c(0.1^3, 0.1^2*0.2*3, 0.2^3, 0.2^3, 1-(0.1^3+0.1^2*0.2*3+0.2^3+0.2^3))
profit = prize -1 

d2 <- data.frame(combi, prize, prob, profit)
d2

exp.each = profit * prob
exp.all = sum(exp.each)
exp.all

var.each = (profit - exp.all)^2 * prob
var.all = sum(var.each)
var.each
var.all
```



p.249

```{r}

```


s an [R Markdown](http://rmarkdown.rstudio.com) Notebook. When you execute code within the notebook, the results appear beneath the code. 

Try executing this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Ctrl+Shift+Enter*. 

```{r}
plot(cars)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
